Quantifying the manageability of pollination networks in an invasion context

### 2017-09-12 paper/manuscript.Rmd
Fix graphs by making unweighted networks

fam <- "Helvetica"
# layout is based on the bidirectional network
set.seed(1)

lay <- bi_net %>%
	layout_nicely()
v_c <- "white"
l_c <- "black"
l_s <- 0.9
ma <- c(0,0,0,0)
label_pos_x <- -1
label_pos_y <- 1

>>>>

fam <- "Helvetica"

# layout is based on the bidirectional network
set.seed(1)
bi_net_uw <- bi_net
E(bi_net_uw)$weight <- 1
lay <- bi_net_uw %>%
	layout_nicely()
v_c <- "white"
l_c <- "black"
l_s <- 0.9
ma <- c(0,0,0,0)
label_pos_x <- -1
label_pos_y <- 1

### 2017-09-12 paper/supporting_information.Rmd
Fix graphs by making unweighted networks

fam <- "Helvetica"
# layout is based on the bidirectional network
set.seed(1)

lay <- bi_net %>%
	layout_nicely()
v_c <- "white"
l_c <- "black"
l_s <- 0.9
ma <- c(0,0,0,0)
label_pos_x <- -1
label_pos_y <- 1

>>>>

fam <- "Helvetica"
# layout is based on the bidirectional network
set.seed(1)
bi_net_uw <- bi_net
E(bi_net_uw)$weight <- 1
lay <- bi_net_uw %>%
	layout_nicely()
v_c <- "white"
l_c <- "black"
l_s <- 0.9
ma <- c(0,0,0,0)
label_pos_x <- -1
label_pos_y <- 1
